Thread Pool in GeckoDB/BOLSTER

### 2018-06-07 Presentations/Milestone3/presentation.tex
Add Evaluation setup to milestone 3

\begin{frame}
	\frametitle{Implementation}
	We...
	\begin{itemize}
		\item Implemented task enqueueing and execution
		\item Implemented performance monitoring as external component
		\item Added gtest framework to project and wrote tests for pool and queue
		\item Started writing performance tests and measures for comparison against baseline ???
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Open issues}
	\begin{itemize}
		\item gtest still has some problems due to itself being implemented in C++
		\item some race condition may still occur
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Task Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			enqueue\_time & Time when the task was enqueued \\
			execution\_time & Time when the task execution begins \\
			complete\_time & Time when the task execution is finished \\
			\hline
		\end{tabular}
		\label{tab2}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Thread Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			waiting\_time & Time the thread spend waiting (ms) \\
			busy\_time & Time the thread spend executing tasks (ms)\\
			task\_count & Number of tasks the thread has executed \\
			\hline
		\end{tabular}
		\label{tab3}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Thread Pool Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			working\_time & Time the thread pool runs (ms) \\
			task\_complete\_count & Number of completed tasks \\
			task\_enqueued\_count & Number of enqueued tasks \\
			avg\_complete\_time & Average time span from enqueueing until \\
			& execution of tasks \\
			avg\_wait\_time & Average time of tasks spend in the queue \\
			\hline
		\end{tabular}
		\label{tab4}
	\end{center}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Implementation}
	We...
	\begin{itemize}
		\item Implemented task enqueueing and execution
		\item Implemented performance monitoring as external component
		\item Added gtest framework to project and wrote tests for pool and queue
		\item Started writing performance tests and measures for comparison against baseline
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Open issues}
	\begin{itemize}
		\item GTest still has some problems with c atomics due to itself being implemented in C++
		\item Some race condition may still occur
		\item Check for memory leaks using valgrind
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Evaluation Setup}
	\begin{itemize}
		\item Use of geckodb to stress test the thread pool by with BOLSTER primitives
		\item Measure different statistics for tasks, thread and thread pools
		\item Use statistics to determine optimal configurations for different thread pool instances
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Task Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			enqueue\_time & Time when the task was enqueued \\
			execution\_time & Time when the task execution begins \\
			complete\_time & Time when the task execution is finished \\
			\hline
		\end{tabular}
		\label{tab2}
	\end{center}
	\begin{itemize}
		\item Minimize waiting time $(execution\_time - enqueue\_time)$
		\item Evaluate the task setup considering the whole processing time 
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Thread Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			waiting\_time & Time the thread spend waiting (ms) \\
			busy\_time & Time the thread spend executing tasks (ms)\\
			task\_count & Number of tasks the thread has executed \\
			\hline
		\end{tabular}
		\label{tab3}
	\end{center}
	\begin{itemize}
		\item $waiting\_time$ of threads indicate a good thread pool size
		\item $task\_count$ interesting to number of all completed tasks
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Thread Pool Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			working\_time & Time the thread pool runs (ms) \\
			task\_complete\_count & Number of completed tasks \\
			task\_enqueued\_count & Number of enqueued tasks \\
			avg\_complete\_time & Average time span from enqueueing until \\
			& execution of tasks \\
			avg\_wait\_time & Average time of tasks spend in the queue \\
			\hline
		\end{tabular}
		\label{tab4}
	\end{center}
	\begin{itemize}
		\item $avg\_wait\_time$ indicates the quality of the chosen thread pool size
	\end{itemize}
\end{frame}
